Multimatrices and Their Derivatives \\ \large An Impractical Guide to Global Conquest

### 2019-07-15 Math/book.tex
Citation for Hadamard Product

\section{Multimatrix Hadamard Product}

\begin{displayquote}
TODO
\end{displayquote}

What the hell is a `Hadamard product'? The Hadamar product of two matricies
is how one would actually expect matrix multiplication to work.

In short, if two matricies, $A$ and $B$ have the same shape,
\[ |A| = |B| = \left<r,c\right> \]
Then their Hadamard Product, $A \bullet B$, is the same shape and each element
is just the product of the corresponding elements of $A$ and $B$. That is,
\[ (A \bullet B)[r,c] = A[r,c] B[r,c] \]

>>>>

\section{Hadamard Product}

What the hell is a `Hadamard product'? The Hadamard product \cite{wiki:hadamard}
of two matricies is how one would actually expect matrix multiplication to work.

In short, if two matricies, $A$ and $B$ have the same shape,
\[ |A| = |B| = \left<r,c\right> \]
Then their Hadamard product, $A \bullet B$, is the same shape and each element
is just the product of the corresponding elements of $A$ and $B$. That is,
\[ (A \bullet B)[r,c] = A[r,c] B[r,c] \]
